Security Metrics for the Android Ecosystem

### 2016-06-07 dastats.tex
Updated figures etc

\newcommand{\daEndDate}{2016-03-13}

@@

\newcommand{\daMeanInsecurityPercNominal}{83.1\%}
\newcommand{\daMeanInsecurityPerc}{$83.1 \pm 0.0\%$}
\newcommand{\daMeanInsecurityPercTwosfNominal}{83\%}
\newcommand{\daMeanInsecurityPercTwosf}{$83 \pm 0\%$}
\newcommand{\daMeanSecurityPercNominal}{16.9\%}
\newcommand{\daMeanSecurityPerc}{$16.9 \pm 0.0\%$}
\newcommand{\daMeanSecurityPercTwosfNominal}{17\%}
\newcommand{\daMeanSecurityPercTwosf}{$17 \pm 0\%$}
\newcommand{\daVulnFreeNominal}{0.169}
\newcommand{\daVulnFree}{$0.169 \pm 0.0$}
\newcommand{\daMeanOutstandingVulnerabilities}{$0.468 \pm 0.0$}

@@

\newcommand{\daSecurityScoreNominal}{3.16}
\newcommand{\daSecurityScore}{$3.16 \pm 0.0$}
\newcommand{\daCurrentMeanInsecurityPercNominal}{63.7\%}
\newcommand{\daCurrentMeanInsecurityPerc}{$63.7 \pm 0.0\%$}
\newcommand{\daCurrentMeanInsecurityPercTwosfNominal}{64\%}
\newcommand{\daCurrentMeanInsecurityPercTwosf}{$64 \pm 0\%$}
\newcommand{\daCurrentMeanSecurityPercNominal}{36.3\%}
\newcommand{\daCurrentMeanSecurityPerc}{$36.3 \pm 0.0\%$}
\newcommand{\daCurrentMeanSecurityPercTwosfNominal}{36\%}
\newcommand{\daCurrentMeanSecurityPercTwosf}{$36 \pm 0\%$}
\newcommand{\daCurrentVulnFreeNominal}{0.363}
\newcommand{\daCurrentVulnFree}{$0.363 \pm 0.0$}
\newcommand{\daCurrentMeanOutstandingVulnerabilities}{$0.0257 \pm 0.0$}
\newcommand{\daCurrentUpdatednessNominal}{0.0963}
\newcommand{\daCurrentUpdatedness}{$0.0963 \pm 0.0$}
\newcommand{\daCurrentUpdatednessPercNominal}{9.63\%}
\newcommand{\daCurrentUpdatednessPerc}{$9.63 \pm 0.0\%$}
\newcommand{\daCurrentUpdatednessPercTwosfNominal}{9.6\%}
\newcommand{\daCurrentUpdatednessPercTwosf}{$9.6 \pm 0.0\%$}
\newcommand{\daCurrentSecurityScoreNominal}{4.7}
\newcommand{\daCurrentSecurityScore}{$4.7 \pm 0.0$}
\newcommand{\daDailyParticipationNominal}{885}
\newcommand{\daDailyParticipation}{$885 \pm 340$}

@@

\newcommand{\daNumPossibleSecurityUpdates}{2\,340}
\newcommand{\daOSCurveFitParamFirst}{81.0}

@@

\newcommand{\daOSCurveHalfDeployedYears}{$0.908 \pm 0.243$}

@@

\newcommand{\daTabSecScoresmanufacturer}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline LG & $0.44 \pm 0.00$ & $0.33 \pm 0.00$ & $0.55 \pm 0.01$ & $4.93 \pm 0.02$ \\  oneplus & $0.88 \pm 0.00$ & $0.31 \pm 0.01$ & $6.95 \pm 0.12$ & $4.44 \pm 0.03$ \\  Motorola & $0.32 \pm 0.00$ & $0.14 \pm 0.00$ & $0.65 \pm 0.01$ & $3.74 \pm 0.02$ \\  Sony & $0.29 \pm 0.00$ & $0.18 \pm 0.00$ & $1.06 \pm 0.02$ & $3.25 \pm 0.02$ \\  Samsung & $0.15 \pm 0.00$ & $0.06 \pm 0.00$ & $0.55 \pm 0.00$ & $2.95 \pm 0.00$ \\  HTC & $0.13 \pm 0.00$ & $0.09 \pm 0.00$ & $0.81 \pm 0.01$ & $2.66 \pm 0.02$ \\  Asus & $0.31 \pm 0.00$ & $0.46 \pm 0.01$ & $5.60 \pm 0.06$ & $2.64 \pm 0.02$ \\  \textit{other} & $0.05 \pm 0.00$ & $0.05 \pm 0.00$ & $0.97 \pm 0.01$ & $2.03 \pm 0.02$ \\  alps & $0.02 \pm 0.00$ & $0.20 \pm 0.01$ & $5.00 \pm 0.10$ & $0.73 \pm 0.02$ \\  Symphony & $0.00 \pm 0.00$ & $0.10 \pm 0.00$ & $5.45 \pm 0.06$ & $0.33 \pm 0.01$ \\  walton & $0.00 \pm 0.00$ & $0.09 \pm 0.00$ & $6.08 \pm 0.08$ & $0.28 \pm 0.01$ \\ \end{tabular} \caption{Security scores for manufacturers} \label{tab:sec_manufacturer} \end{table*}}

@@

\newcommand{\daSecScoreBestmanufacturerScoreNominal}{4.93}
\newcommand{\daSecScoreBestmanufacturerScore}{$4.93 \pm 0.0$}

@@

\newcommand{\daTabSecScoresmodel}{\begin{table*} \centering \begin{tabular}{l|l|c|c|c|c} Made by & Model name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline LG & Nexus 5 & $0.78 \pm 0.00$ & $0.65 \pm 0.01$ & $6.02 \pm 0.09$ & $5.10 \pm 0.03$ \\  Samsung & Galaxy Nexus & $0.51 \pm 0.00$ & $0.53 \pm 0.01$ & $1.50 \pm 0.04$ & $4.75 \pm 0.05$ \\  LG & Nexus 4 & $0.60 \pm 0.00$ & $0.57 \pm 0.01$ & $5.52 \pm 0.08$ & $4.16 \pm 0.03$ \\  Asus & Nexus 7 & $0.46 \pm 0.00$ & $0.67 \pm 0.01$ & $5.69 \pm 0.08$ & $3.87 \pm 0.03$ \\  \textit{unknown} & \textit{other} & $0.14 \pm 0.00$ & $0.13 \pm 0.00$ & $0.54 \pm 0.00$ & $3.15 \pm 0.00$ \\  HTC & HTC Desire & $0.14 \pm 0.00$ & $0.07 \pm 0.01$ & $0.51 \pm 0.03$ & $3.03 \pm 0.05$ \\  HTC & Desire HD & $0.09 \pm 0.00$ & $0.05 \pm 0.00$ & $0.43 \pm 0.03$ & $2.86 \pm 0.04$ \\  Samsung & GT-I9000 & $0.03 \pm 0.00$ & $0.03 \pm 0.00$ & $0.44 \pm 0.04$ & $2.55 \pm 0.05$ \\  HTC & HTC Sensation & $0.34 \pm 0.00$ & $0.01 \pm 0.01$ & $1.49 \pm 0.06$ & $2.49 \pm 0.06$ \\  Motorola & DROIDX & $0.02 \pm 0.00$ & $0.04 \pm 0.01$ & $0.55 \pm 0.04$ & $2.39 \pm 0.06$ \\  Samsung & GT-I9100 & $0.21 \pm 0.00$ & $0.01 \pm 0.00$ & $1.26 \pm 0.02$ & $2.23 \pm 0.02$ \\  HTC & HTC Desire S & $0.02 \pm 0.00$ & $0.02 \pm 0.00$ & $1.00 \pm 0.08$ & $1.75 \pm 0.09$ \\  HTC & HTC One & $0.10 \pm 0.00$ & $0.38 \pm 0.01$ & $5.75 \pm 0.12$ & $1.56 \pm 0.04$ \\  Samsung & GT-N7000 & $0.25 \pm 0.00$ & $0.00 \pm 0.00$ & $2.46 \pm 0.05$ & $1.46 \pm 0.03$ \\  Samsung & GT-P1000 & $0.01 \pm 0.00$ & $0.00 \pm 0.01$ & $1.87 \pm 0.06$ & $0.84 \pm 0.05$ \\  Samsung & GT-I9505 & $0.10 \pm 0.00$ & $0.13 \pm 0.00$ & $6.79 \pm 0.07$ & $0.79 \pm 0.02$ \\  Samsung & SM-N9005 & $0.07 \pm 0.00$ & $0.15 \pm 0.01$ & $7.17 \pm 0.18$ & $0.72 \pm 0.03$ \\  Samsung & GT-I9300 & $0.14 \pm 0.00$ & $0.02 \pm 0.00$ & $6.26 \pm 0.05$ & $0.63 \pm 0.01$ \\  HTC & HTC Desire HD & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & $3.03 \pm 0.05$ & $0.28 \pm 0.03$ \\  Samsung & GT-N7100 & $0.05 \pm 0.00$ & $0.00 \pm 0.01$ & $6.64 \pm 0.09$ & $0.21 \pm 0.02$ \\  Symphony & Symphony W68 & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & $11.00 \pm 0.13$ & $0.00 \pm 0.03$ \\ \end{tabular} \caption{Security scores for models} \label{tab:sec_model} \end{table*}}

@@

\newcommand{\daSecScoreBestmodelScoreNominal}{5.1}
\newcommand{\daSecScoreBestmodelScore}{$5.1 \pm 0.0$}

@@

\newcommand{\daTabSecScoressummary}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline Nexus devices & $0.62 \pm 0.00$ & $0.50 \pm 0.00$ & $0.50 \pm 0.01$ & $6.26 \pm 0.02$ \\  non-Nexus & $0.13 \pm 0.00$ & $0.02 \pm 0.00$ & $0.54 \pm 0.00$ & $2.81 \pm 0.00$ \\ \end{tabular} \caption{Security scores for Nexus} \label{tab:sec_summary} \end{table*}}
\newcommand{\daTabSecScoresoperator}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline T-Mobile & $0.31 \pm 0.00$ & $0.17 \pm 0.00$ & $0.35 \pm 0.01$ & $4.24 \pm 0.02$ \\  O2 uk & $0.31 \pm 0.00$ & $0.12 \pm 0.00$ & $0.30 \pm 0.01$ & $4.15 \pm 0.02$ \\  Sprint & $0.23 \pm 0.00$ & $0.12 \pm 0.00$ & $0.30 \pm 0.01$ & $3.85 \pm 0.02$ \\  Orange & $0.23 \pm 0.00$ & $0.11 \pm 0.00$ & $0.34 \pm 0.02$ & $3.75 \pm 0.04$ \\  3 & $0.24 \pm 0.00$ & $0.11 \pm 0.00$ & $0.36 \pm 0.02$ & $3.72 \pm 0.03$ \\  AT\&T & $0.20 \pm 0.00$ & $0.09 \pm 0.00$ & $0.37 \pm 0.01$ & $3.53 \pm 0.02$ \\  Verizon & $0.25 \pm 0.00$ & $0.08 \pm 0.00$ & $0.58 \pm 0.01$ & $3.38 \pm 0.02$ \\  \textit{unknown} & $0.18 \pm 0.00$ & $0.19 \pm 0.00$ & $0.73 \pm 0.01$ & $3.26 \pm 0.02$ \\  Vodafone uk & $0.14 \pm 0.00$ & $0.14 \pm 0.00$ & $0.54 \pm 0.03$ & $3.18 \pm 0.04$ \\  n Telenor & $0.09 \pm 0.00$ & $0.13 \pm 0.00$ & $1.17 \pm 0.02$ & $2.19 \pm 0.02$ \\  Airtel & $0.05 \pm 0.00$ & $0.04 \pm 0.00$ & $2.48 \pm 0.04$ & $0.78 \pm 0.02$ \\  Grameenphone & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & $2.72 \pm 0.03$ & $0.51 \pm 0.01$ \\  Robi & $0.00 \pm 0.00$ & $0.08 \pm 0.00$ & $3.13 \pm 0.05$ & $0.50 \pm 0.02$ \\  banglalink & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & $3.12 \pm 0.05$ & $0.37 \pm 0.01$ \\ \end{tabular} \caption{Security scores for operators} \label{tab:sec_operator} \end{table*}}
\newcommand{\daSecScoreBestoperator}{T-Mobile}
\newcommand{\daSecScoreBestoperatorScoreNominal}{4.24}
\newcommand{\daSecScoreBestoperatorScore}{$4.24 \pm 0.0$}
\newcommand{\daSecScoreBestoperatorNumFullVersions}{201}

@@

\newcommand{\daTabDLDistances}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & Nexus \\ \hline equal & 0.0 & 0.0476 & 0.0714 & 0.0 \\weight $u$ & 0.0909 & 0.0952 & 0.143 & 0.0 \\weight $m$ & 0.273 & 0.286 & 0.0714 & 0.0 \\$f$ & 0.273 & 0.81 & 0.357 & 0.0 \\$m$ & 0.636 & 0.857 & 0.429 & 0.0 \\$u$ & 0.818 & 0.714 & 0.786 & 0.0 \\\end{tabular} \caption{Normalised Damerau-Levenshtein distances for different metrics} \label{tab:dl_distances} \end{table}}
\newcommand{\daTabChangeInScores}{\begin{table*}\small \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & Nexus \\ \hline $m$ & $-0.968 \pm 2.81$ & $-0.75 \pm 3.09$ & $-3.06 \pm 1.75$ & $-2.94 \pm 2.33$ \\weight $m$ & $-0.116 \pm 0.426$ & $-0.095 \pm 0.446$ & $-0.413 \pm 0.228$ & $-0.369 \pm 0.346$ \\equal & $-0.0211 \pm 0.18$ & $-0.0223 \pm 0.163$ & $-0.119 \pm 0.064$ & $-0.0839 \pm 0.126$ \\weight $u$ & $0.0524 \pm 0.208$ & $0.0282 \pm 0.15$ & $0.057 \pm 0.101$ & $0.118 \pm 0.019$ \\$f$ & $0.19 \pm 1.62$ & $0.201 \pm 1.36$ & $1.07 \pm 0.50$ & $0.755 \pm 1.04$ \\$u$ & $0.715 \pm 1.54$ & $0.482 \pm 1.65$ & $1.64 \pm 1.21$ & $1.93 \pm 0.96$ \\\end{tabular} \caption{Mean change in scores for different metrics} \label{tab:change_in_scores} \end{table*}}

@@

\newcommand{\daNumUpdatesBigUpgrades}{890}

@@

\newcommand{\daNumDataPoints}{58 billion}

@@

\newcommand{\daMeanOutstandingVulnerabilitiesNominal}{0.468}
\newcommand{\daCurrentMeanOutstandingVulnerabilitiesNominal}{0.0257}

@@

\newcommand{\daTabSpearmanRanks}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & Nexus \\ $\pm\sigma$ & 0.2 & 0.141 & 0.175 & 0.632 \\ \hline $u$ & 0.436 & 0.705 & 0.552 & 1.0 \\$m$ & 0.455 & 0.517 & 0.952 & 1.0 \\$f$ & 0.936 & 0.694 & 0.938 & 1.0 \\weight $m$ & 0.973 & 0.978 & 0.996 & 1.0 \\weight $u$ & 0.991 & 0.997 & 0.991 & 1.0 \\equal & 1.0 & 0.999 & 0.996 & 1.0 \\\end{tabular} \caption{Spearman Rank correlation coefficients for different metrics. The uncertainty is constant for each column but does not take into account the uncertainty in the score which produced the ranking.} \label{tab:spearman_ranks} \end{table}}

@@

\newcommand{\daSecScoreBestsummaryScoreNominal}{6.26}
\newcommand{\daSecScoreBestsummaryScore}{$6.26 \pm 0.0$}

@@

\newcommand{\daSecScoreWorstsummaryScoreNominal}{2.81}
\newcommand{\daSecScoreWorstsummaryScore}{$2.81 \pm 0.0$}

@@

\newcommand{\daMeanDefInsecurityPercNominal}{70.9\%}
\newcommand{\daMeanDefInsecurityPerc}{$70.9 \pm 0.0\%$}
\newcommand{\daMeanDefInsecurityPercTwosfNominal}{71\%}
\newcommand{\daMeanDefInsecurityPercTwosf}{$71 \pm 0\%$}
\newcommand{\daMeanMaybeSecurePercNominal}{14.6\%}
\newcommand{\daMeanMaybeSecurePerc}{$14.6 \pm 0.0\%$}
\newcommand{\daMeanMaybeSecurePercTwosfNominal}{15\%}
\newcommand{\daMeanMaybeSecurePercTwosf}{$15 \pm 0\%$}
\newcommand{\daOptSecurityScoreNominal}{3.64}
\newcommand{\daOptSecurityScore}{$3.64 \pm 0.0$}
\newcommand{\daCurrentMeanDefInsecurityPercNominal}{58.1\%}
\newcommand{\daCurrentMeanDefInsecurityPerc}{$58.1 \pm 0.0\%$}
\newcommand{\daCurrentMeanDefInsecurityPercTwosfNominal}{58\%}
\newcommand{\daCurrentMeanDefInsecurityPercTwosf}{$58 \pm 0\%$}

>>>>

\newcommand{\daEndDate}{2016-03-16}

@@

\newcommand{\daMeanInsecurityPercNominal}{87.6\%}
\newcommand{\daMeanInsecurityPerc}{$87.6 \pm 0.0\%$}
\newcommand{\daMeanInsecurityPercTwosfNominal}{88\%}
\newcommand{\daMeanInsecurityPercTwosf}{$88 \pm 0\%$}
\newcommand{\daMeanSecurityPercNominal}{12.4\%}
\newcommand{\daMeanSecurityPerc}{$12.4 \pm 0.0\%$}
\newcommand{\daMeanSecurityPercTwosfNominal}{12\%}
\newcommand{\daMeanSecurityPercTwosf}{$12 \pm 0\%$}
\newcommand{\daVulnFreeNominal}{0.124}
\newcommand{\daVulnFree}{$0.124 \pm 0.0$}
\newcommand{\daMeanOutstandingVulnerabilities}{$0.661 \pm 0.0$}

@@

\newcommand{\daSecurityScoreNominal}{2.71}
\newcommand{\daSecurityScore}{$2.71 \pm 0.0$}
\newcommand{\daCurrentMeanInsecurityPercNominal}{85.2\%}
\newcommand{\daCurrentMeanInsecurityPerc}{$85.2 \pm 0.0\%$}
\newcommand{\daCurrentMeanInsecurityPercTwosfNominal}{85\%}
\newcommand{\daCurrentMeanInsecurityPercTwosf}{$85 \pm 0\%$}
\newcommand{\daCurrentMeanSecurityPercNominal}{14.8\%}
\newcommand{\daCurrentMeanSecurityPerc}{$14.8 \pm 0.1\%$}
\newcommand{\daCurrentMeanSecurityPercTwosfNominal}{15\%}
\newcommand{\daCurrentMeanSecurityPercTwosf}{$15 \pm 0\%$}
\newcommand{\daCurrentVulnFreeNominal}{0.148}
\newcommand{\daCurrentVulnFree}{$0.148 \pm 0.001$}
\newcommand{\daCurrentMeanOutstandingVulnerabilities}{$0.397 \pm 0.0$}
\newcommand{\daCurrentUpdatednessNominal}{0.0951}
\newcommand{\daCurrentUpdatedness}{$0.0951 \pm 0.0$}
\newcommand{\daCurrentUpdatednessPercNominal}{9.51\%}
\newcommand{\daCurrentUpdatednessPerc}{$9.51 \pm 0.0\%$}
\newcommand{\daCurrentUpdatednessPercTwosfNominal}{9.5\%}
\newcommand{\daCurrentUpdatednessPercTwosf}{$9.5 \pm 0.0\%$}
\newcommand{\daCurrentSecurityScoreNominal}{3.29}
\newcommand{\daCurrentSecurityScore}{$3.29 \pm 0.0$}
\newcommand{\daDailyParticipationNominal}{884}
\newcommand{\daDailyParticipation}{$884 \pm 341$}

@@

\newcommand{\daNumPossibleSecurityUpdates}{2\,860}
\newcommand{\daOSCurveFitParamFirst}{80.9}

@@

\newcommand{\daOSCurveHalfDeployedYears}{$0.908 \pm 0.242$}

@@

\newcommand{\daTabSecScoresmanufacturer}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline LG & $0.34 \pm 0.00$ & $0.33 \pm 0.00$ & $0.74 \pm 0.01$ & $4.28 \pm 0.02$ \\  Motorola & $0.26 \pm 0.00$ & $0.14 \pm 0.00$ & $0.65 \pm 0.01$ & $3.50 \pm 0.02$ \\  HTC & $0.13 \pm 0.00$ & $0.09 \pm 0.00$ & $0.87 \pm 0.01$ & $2.59 \pm 0.02$ \\  Sony & $0.13 \pm 0.00$ & $0.18 \pm 0.00$ & $1.09 \pm 0.02$ & $2.57 \pm 0.02$ \\  Asus & $0.23 \pm 0.00$ & $0.46 \pm 0.01$ & $5.61 \pm 0.06$ & $2.29 \pm 0.02$ \\  Samsung & $0.11 \pm 0.00$ & $0.06 \pm 0.00$ & $0.99 \pm 0.00$ & $2.24 \pm 0.00$ \\  \textit{other} & $0.04 \pm 0.00$ & $0.05 \pm 0.00$ & $1.14 \pm 0.01$ & $1.79 \pm 0.02$ \\  oneplus & $0.02 \pm 0.00$ & $0.31 \pm 0.01$ & $7.85 \pm 0.13$ & $1.00 \pm 0.02$ \\  alps & $0.02 \pm 0.00$ & $0.20 \pm 0.01$ & $5.00 \pm 0.10$ & $0.73 \pm 0.02$ \\  Symphony & $0.00 \pm 0.00$ & $0.10 \pm 0.00$ & $5.74 \pm 0.06$ & $0.32 \pm 0.01$ \\  walton & $0.00 \pm 0.00$ & $0.09 \pm 0.00$ & $6.08 \pm 0.08$ & $0.28 \pm 0.01$ \\ \end{tabular} \caption{Security scores for manufacturers} \label{tab:sec_manufacturer} \end{table*}}

@@

\newcommand{\daSecScoreBestmanufacturerScoreNominal}{4.28}
\newcommand{\daSecScoreBestmanufacturerScore}{$4.28 \pm 0.0$}

@@

\newcommand{\daTabSecScoresmodel}{\begin{table*} \centering \begin{tabular}{l|l|c|c|c|c} Made by & Model name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline LG & Nexus 5 & $0.71 \pm 0.00$ & $0.65 \pm 0.01$ & $6.09 \pm 0.09$ & $4.80 \pm 0.03$ \\  Samsung & Galaxy Nexus & $0.51 \pm 0.00$ & $0.53 \pm 0.01$ & $1.50 \pm 0.04$ & $4.74 \pm 0.05$ \\  Asus & Nexus 7 & $0.34 \pm 0.00$ & $0.67 \pm 0.01$ & $5.69 \pm 0.08$ & $3.39 \pm 0.03$ \\  LG & Nexus 4 & $0.36 \pm 0.00$ & $0.57 \pm 0.01$ & $5.52 \pm 0.08$ & $3.21 \pm 0.03$ \\  HTC & HTC Desire & $0.14 \pm 0.00$ & $0.07 \pm 0.01$ & $0.51 \pm 0.03$ & $3.03 \pm 0.05$ \\  HTC & Desire HD & $0.09 \pm 0.00$ & $0.05 \pm 0.00$ & $0.43 \pm 0.03$ & $2.86 \pm 0.04$ \\  \textit{unknown} & \textit{other} & $0.08 \pm 0.00$ & $0.13 \pm 0.00$ & $0.74 \pm 0.00$ & $2.65 \pm 0.00$ \\  Samsung & GT-I9000 & $0.03 \pm 0.00$ & $0.03 \pm 0.00$ & $0.44 \pm 0.04$ & $2.55 \pm 0.05$ \\  HTC & HTC Sensation & $0.34 \pm 0.00$ & $0.01 \pm 0.01$ & $1.49 \pm 0.06$ & $2.49 \pm 0.06$ \\  Motorola & DROIDX & $0.02 \pm 0.00$ & $0.04 \pm 0.01$ & $0.55 \pm 0.04$ & $2.39 \pm 0.06$ \\  Samsung & GT-I9100 & $0.21 \pm 0.00$ & $0.01 \pm 0.00$ & $1.26 \pm 0.02$ & $2.23 \pm 0.02$ \\  HTC & HTC Desire S & $0.02 \pm 0.00$ & $0.02 \pm 0.00$ & $1.00 \pm 0.08$ & $1.75 \pm 0.09$ \\  HTC & HTC One & $0.10 \pm 0.00$ & $0.38 \pm 0.01$ & $6.08 \pm 0.12$ & $1.56 \pm 0.04$ \\  Samsung & GT-N7000 & $0.25 \pm 0.00$ & $0.00 \pm 0.00$ & $2.46 \pm 0.05$ & $1.46 \pm 0.03$ \\  Samsung & GT-P1000 & $0.01 \pm 0.00$ & $0.00 \pm 0.01$ & $1.87 \pm 0.06$ & $0.84 \pm 0.05$ \\  Samsung & GT-I9505 & $0.07 \pm 0.00$ & $0.13 \pm 0.00$ & $7.03 \pm 0.07$ & $0.70 \pm 0.01$ \\  Samsung & SM-N9005 & $0.05 \pm 0.00$ & $0.15 \pm 0.01$ & $8.65 \pm 0.20$ & $0.65 \pm 0.03$ \\  Samsung & GT-I9300 & $0.14 \pm 0.00$ & $0.02 \pm 0.00$ & $6.46 \pm 0.05$ & $0.62 \pm 0.01$ \\  HTC & HTC Desire HD & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & $3.03 \pm 0.05$ & $0.28 \pm 0.03$ \\  Samsung & GT-N7100 & $0.05 \pm 0.00$ & $0.00 \pm 0.01$ & $6.64 \pm 0.09$ & $0.21 \pm 0.02$ \\  Symphony & Symphony W68 & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & $11.00 \pm 0.13$ & $0.00 \pm 0.03$ \\ \end{tabular} \caption{Security scores for models} \label{tab:sec_model} \end{table*}}

@@

\newcommand{\daSecScoreBestmodelScoreNominal}{4.8}
\newcommand{\daSecScoreBestmodelScore}{$4.8 \pm 0.0$}

@@

\newcommand{\daTabSecScoressummary}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline Nexus devices & $0.53 \pm 0.00$ & $0.50 \pm 0.00$ & $0.69 \pm 0.01$ & $5.63 \pm 0.02$ \\  non-Nexus & $0.09 \pm 0.00$ & $0.02 \pm 0.00$ & $0.74 \pm 0.00$ & $2.35 \pm 0.00$ \\ \end{tabular} \caption{Security scores for Nexus} \label{tab:sec_summary} \end{table*}}
\newcommand{\daTabSecScoresoperator}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline O2 uk & $0.27 \pm 0.00$ & $0.12 \pm 0.00$ & $0.30 \pm 0.01$ & $3.97 \pm 0.02$ \\  Sprint & $0.19 \pm 0.00$ & $0.12 \pm 0.00$ & $0.30 \pm 0.01$ & $3.67 \pm 0.02$ \\  T-Mobile & $0.21 \pm 0.00$ & $0.17 \pm 0.00$ & $0.56 \pm 0.02$ & $3.56 \pm 0.03$ \\  3 & $0.16 \pm 0.00$ & $0.11 \pm 0.00$ & $0.36 \pm 0.02$ & $3.44 \pm 0.03$ \\  Orange & $0.20 \pm 0.00$ & $0.11 \pm 0.00$ & $0.53 \pm 0.03$ & $3.35 \pm 0.04$ \\  AT\&T & $0.12 \pm 0.00$ & $0.09 \pm 0.00$ & $0.37 \pm 0.01$ & $3.20 \pm 0.02$ \\  Vodafone uk & $0.11 \pm 0.00$ & $0.14 \pm 0.00$ & $0.54 \pm 0.03$ & $3.08 \pm 0.04$ \\  Verizon & $0.16 \pm 0.00$ & $0.08 \pm 0.00$ & $0.58 \pm 0.01$ & $3.04 \pm 0.02$ \\  \textit{unknown} & $0.12 \pm 0.00$ & $0.19 \pm 0.00$ & $1.01 \pm 0.02$ & $2.66 \pm 0.02$ \\  n Telenor & $0.06 \pm 0.00$ & $0.13 \pm 0.00$ & $1.31 \pm 0.02$ & $1.93 \pm 0.02$ \\  Airtel & $0.05 \pm 0.00$ & $0.04 \pm 0.00$ & $2.48 \pm 0.04$ & $0.76 \pm 0.02$ \\  Robi & $0.00 \pm 0.00$ & $0.09 \pm 0.00$ & $3.14 \pm 0.05$ & $0.51 \pm 0.02$ \\  Grameenphone & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & $3.08 \pm 0.03$ & $0.40 \pm 0.01$ \\  banglalink & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & $3.12 \pm 0.05$ & $0.37 \pm 0.01$ \\ \end{tabular} \caption{Security scores for operators} \label{tab:sec_operator} \end{table*}}
\newcommand{\daSecScoreBestoperator}{O2 uk}
\newcommand{\daSecScoreBestoperatorScoreNominal}{3.97}
\newcommand{\daSecScoreBestoperatorScore}{$3.97 \pm 0.0$}
\newcommand{\daSecScoreBestoperatorNumFullVersions}{124}

@@

\newcommand{\daTabDLDistances}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & Nexus \\ \hline equal & 0.0909 & 0.143 & 0.0 & 0.0 \\weight $u$ & 0.0909 & 0.143 & 0.0 & 0.0 \\weight $m$ & 0.182 & 0.381 & 0.143 & 0.0 \\$f$ & 0.273 & 0.762 & 0.571 & 0.0 \\$m$ & 0.636 & 0.857 & 0.429 & 0.0 \\$u$ & 0.909 & 0.762 & 0.857 & 0.0 \\\end{tabular} \caption{Normalised Damerau-Levenshtein distances for different metrics} \label{tab:dl_distances} \end{table}}
\newcommand{\daTabChangeInScores}{\begin{table*}\small \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & Nexus \\ \hline $m$ & $-1.21 \pm 2.08$ & $-0.819 \pm 2.93$ & $-3.03 \pm 1.84$ & $-2.58 \pm 2.2$ \\weight $m$ & $-0.201 \pm 0.249$ & $-0.116 \pm 0.412$ & $-0.426 \pm 0.25$ & $-0.347 \pm 0.314$ \\equal & $-0.0894 \pm 0.0513$ & $-0.0377 \pm 0.147$ & $-0.137 \pm 0.077$ & $-0.0991 \pm 0.105$ \\weight $u$ & $-0.0671 \pm 0.128$ & $0.00267 \pm 0.17$ & $0.0162 \pm 0.0816$ & $0.0494 \pm 0.0373$ \\$u$ & $0.134 \pm 1.58$ & $0.366 \pm 1.78$ & $1.39 \pm 1.11$ & $1.39 \pm 1.08$ \\$f$ & $0.804 \pm 0.462$ & $0.34 \pm 1.21$ & $1.23 \pm 0.61$ & $0.892 \pm 0.84$ \\\end{tabular} \caption{Mean change in scores for different metrics} \label{tab:change_in_scores} \end{table*}}

@@

\newcommand{\daNumUpdatesBigUpgrades}{891}

@@

\newcommand{\daNumDataPoints}{44 billion}

@@

\newcommand{\daMeanOutstandingVulnerabilitiesNominal}{0.661}
\newcommand{\daCurrentMeanOutstandingVulnerabilitiesNominal}{0.397}

@@

\newcommand{\daTabSpearmanRanks}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & Nexus \\ $\pm\sigma$ & 0.2 & 0.141 & 0.175 & 0.632 \\ \hline $u$ & 0.3 & 0.712 & 0.552 & 1.0 \\$m$ & 0.855 & 0.517 & 0.934 & 1.0 \\$f$ & 0.964 & 0.694 & 0.943 & 1.0 \\weight $m$ & 0.973 & 0.948 & 0.991 & 1.0 \\equal & 0.991 & 0.996 & 1.0 & 1.0 \\weight $u$ & 0.991 & 0.996 & 1.0 & 1.0 \\\end{tabular} \caption{Spearman Rank correlation coefficients for different metrics. The uncertainty is constant for each column but does not take into account the uncertainty in the score which produced the ranking.} \label{tab:spearman_ranks} \end{table}}

@@

\newcommand{\daSecScoreBestsummaryScoreNominal}{5.63}
\newcommand{\daSecScoreBestsummaryScore}{$5.63 \pm 0.0$}

@@

\newcommand{\daSecScoreWorstsummaryScoreNominal}{2.35}
\newcommand{\daSecScoreWorstsummaryScore}{$2.35 \pm 0.0$}

@@

\newcommand{\daMeanDefInsecurityPercNominal}{73.2\%}
\newcommand{\daMeanDefInsecurityPerc}{$73.2 \pm 0.0\%$}
\newcommand{\daMeanDefInsecurityPercTwosfNominal}{73\%}
\newcommand{\daMeanDefInsecurityPercTwosf}{$73 \pm 0\%$}
\newcommand{\daMeanMaybeSecurePercNominal}{16.4\%}
\newcommand{\daMeanMaybeSecurePerc}{$16.4 \pm 0.0\%$}
\newcommand{\daMeanMaybeSecurePercTwosfNominal}{16\%}
\newcommand{\daMeanMaybeSecurePercTwosf}{$16 \pm 0\%$}
\newcommand{\daOptSecurityScoreNominal}{3.29}
\newcommand{\daOptSecurityScore}{$3.29 \pm 0.0$}
\newcommand{\daCurrentMeanDefInsecurityPercNominal}{69.4\%}
\newcommand{\daCurrentMeanDefInsecurityPerc}{$69.4 \pm 0.0\%$}
\newcommand{\daCurrentMeanDefInsecurityPercTwosfNominal}{69\%}
\newcommand{\daCurrentMeanDefInsecurityPercTwosf}{$69 \pm 0\%$}
\newcommand{\daCurrentMeanMaybeSecurePercNominal}{19.1\%}
